Carbonate chemistry at Ny-Ålesund

### 2023-05-29 awipev-CO2.Rmd
Kdrive path

#export latex table
tables_path <- "~/kDrive/Documents/publications/publications_inpreparation/gattuso_etal_awipev-CO2/paper/tables/"
knitr::kable(diff_table_pco2_at, digits = 3, caption = "Difference between spectrophotometric pH and pH calculated with pCO2 and AT using different formulations for K1 and K2.", format = "latex") %>% 
kableExtra::save_kable(file=paste0(tables_path,"diff_table_pco2_at.tex"))
```
**_Comparison of various formulations compared to Lueker et al. (2000)_**

@@

#export latex table
tables_path <- "~/kDrive/Documents/publications/publications_inpreparation/gattuso_etal_awipev-CO2/paper/tables/"
knitr::kable(diff_table_at_ct, digits = 3, caption = "Difference between spectrophotometric pH and pH calculated with AT and CT using different formulations for K1 and K2.", format = "latex") %>% 
kableExtra::save_kable(file=paste0(tables_path,"diff_table_at_ct.tex"))
```

>>>>

#export latex table
tables_path <- "/Users/gattuso/kDrive/Documents/publications/publications_submitted/2023_gattuso_etal_essd/revised/tables"
knitr::kable(diff_table_pco2_at, digits = 3, caption = "Difference between spectrophotometric pH and pH calculated with pCO2 and AT using different formulations for K1 and K2.", format = "latex") %>% 
kableExtra::save_kable(file=paste0(tables_path,"diff_table_pco2_at.tex"))
```
**_Comparison of various formulations compared to Lueker et al. (2000)_**

@@

#export latex table
tables_path <- "/Users/gattuso/kDrive/Documents/publications/publications_submitted/2023_gattuso_etal_essd/revised/tables"
knitr::kable(diff_table_at_ct, digits = 3, caption = "Difference between spectrophotometric pH and pH calculated with AT and CT using different formulations for K1 and K2.", format = "latex") %>% 
kableExtra::save_kable(file=paste0(tables_path,"diff_table_at_ct.tex"))
```
